WHITE WINE DATASET EDA by OLGA DERNOVSKA
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2)
library(grid)
library(gridExtra)
library('GGally')
library(reshape2)

```

In the beginning of the project, before starting our analysis, let's take a look 
at our dataset to see its structure, brief view of the dataset and general 
statistics for each variable.

```{r echo=FALSE, echo=FALSE, message=FALSE, warning=FALSE, Load_the_Data}
# Load the Data
wine <- read.csv('wineQualityWhites.csv')
str(wine)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
head(wine)
```


```{r echo=FALSE, Univariate_Plots}
summary(wine)
```

**General information about dataset**
The dataset is related to white variants of the Portuguese "Vinho Verde" wine.

The dataset has 4898 observations for 14 variables. One variable (x) is for 
numeration, 12 input variables include objective tests and the output variable 
'quality' is based on sensory data (median of at least 3 evaluations made by 
wine experts). There are no missing values in the dataset.

Input variables.
Fixed acidity (tartaric acid - g / dm^3): 
most acids involved with wine or fixed or nonvolatile

Volatile acidity (acetic acid - g / dm^3): the amount of acetic acid in wine, 
which at too high of levels can lead to an unpleasant, vinegar taste.
In our dataset we have range from 0.08 to 1.1 with 50% of wines to be in range 
0.21 to 0.32

Citric acid (g / dm^3): 
found in small quantities, citric acid can add 'freshness' and flavor to wines.
In our dataset we have range from 0 to 1.66.

Residual sugar (g / dm^3): the amount of sugar remaining after fermentation 
stops, it's rare to find wines with less than 1 gram/liter.
Wines with greater than 45 grams/liter are considered sweet. 
In our dataset we have range from 0.6 to 65.8. 
We can explore this variable in details.

Chlorides (sodium chloride - g / dm^3): the amount of salt in the wine

Free sulfur dioxide (mg / dm^3): it prevents microbial growth and the 
oxidation of wine

Total sulfur dioxide (mg / dm^3): amount of free and bound forms of S02; 
in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 
concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine.
In our dataset we have range from 9 to 440, which is much higher than 50, so we
can explore this variable.

Density (g / cm^3): is close to that of water depending on the percent alcohol
and sugar content In our dataset we have range from 0.9871 to 1.0390. 
Indeed, it is close to the density of water (1.0)

PH: describes how acidic or basic a wine is on a scale from 0 (very acidic) to 
14 (very basic); most wines are between 3-4 on the pH scale
In our dataset we have range from 2.72 to 3.82, which is really close and most
probably will have no difference.

Sulphates (potassium sulphate - g / dm3): a wine additive which can contribute
to sulfur dioxide gas (S02) levels, which acts as an antimicrobial and 
antioxidant.
In our dataset we have range from 0.22 to 1.08

Alcohol: the percent alcohol content of the wine
In our dataset we have range from 8.0 to 14.2
It is rather wide range for wine, so we can explore this variable in details.

Output variable: 
Quality (score between 0 and 10)
In our dataset we have range from 3 to 9 with 50% of observations to lay
between 5 and 6.


# Univariate Plots Section

#### Explore distribution of quality

```{r echo=FALSE, message=FALSE, warning=FALSE}

qplot(x = quality, data = wine, binwidth = 0.5)

```

We can see that most of our wines (about 50%) have quality 6, many wines are 5 
and 7, few wines are 3, 4, 8 and 9.
Quality is a discrete variable, but we can see its distribution is close to 
normal, there are no outliers and no gaps in the distribution, but poor and high
quality wines are few.

#### Explore distribution of residual sugar - sweetness of wine

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x = residual.sugar, data = wine, binwidth = 1)
```

The distribution of residual sugar is right-skewed, with most of the values 
to be under 20. Values which are more than 20 are few. 
Let's take a look at them closely:

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x = residual.sugar, data = subset(wine, residual.sugar >=20), binwidth = 1)
```

There is only one wine with sugar content around 66, all others are under 33. 
This observation is an outlier, and I will remove it from my dataset.

```{r echo=FALSE, message=FALSE, warning=FALSE}
wine_new <- subset(wine, residual.sugar < 33)
dim(wine_new)
```

As we can see, now there are 4897 observations in our dataset.

Now we can group our wines into categories depending on residual sugar. 
According to EU regulation 753/2002, the following terms may be used on the 
labels of table wines and quality wines:
Dry - up to 4 g/l, if balanced with suitable acidity - up to 9 g/l
Medium Dry - up to 12 g/l, if balanced with suitable acidity - up to 18 g/l
Medium- up to 45 g/l
Sweet - more than 45 g/l
Let's consider, that our wines are balanced, and use levels 9 g/l and 18 g/l
for groupping the wines. 
New variable will take the name 'category'.

```{r echo=FALSE, message=FALSE, warning=FALSE}
wine_new$category = NA
wine_new$category <- ifelse(wine_new$residual.sugar < 9, '1 - dry', 
                        ifelse(wine_new$residual.sugar >= 9 & 
                                 wine_new$residual.sugar<18, 
                               '2 - medium dry', '3 - medium'))
qplot(data = wine_new, x = category)

```

As mentioned before, most of the wines are dry, and it is normal for 
south-european wines. 
 
#### Explore alcohol content distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}

qplot(x = alcohol, data = wine_new, binwidth = 0.2)

```

The distribution of alcohol is slightly right skewed, without long tail, but 
with big difference on the left side. In the beginning of the x-scale there are 
only few observations, then a gap, then again only few, and then bins are high 
with 100, 200 and more observations. This abrupt end can possible have influence 
for our visualizations, so we need to keep it in mind in future explorations. 
From the other side, I would not like to delete it as it is not an outlier, and 
it's value is normal for wines.

#### Explore pH distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}

qplot(x = pH, data = wine_new, binwidth = 0.05)
```

PH is normally distributed, its range is narrow and very common for wines, so we
can consider that all our wine has normal pH levels and won't explore it deeper.

#### Explore volatile acidity distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x = volatile.acidity, data = wine_new, binwidth = 0.02)
```

Distribution of volatile acidity  is slightly right-skewed. We could say, 
that it is normally distributed till approx. 0.5 and then has a tail.
It happens to be range of 0.6 to 0.9 of volatile acidity, which the human 
threshold can detect. Volatile acidity imparts a racy, balsamic edge to a wine.
I will explore the impact of this variable on quality in later analysis.

#### Explore total sulfur dioxide distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}

qplot(x = total.sulfur.dioxide, data = wine_new, binwidth = 10)
```

We can see normal distribution for this variable. 
In later analysis we will check if it has any influence on the quality.

#### Explore density distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x = density, data = wine_new, binwidth = 0.0005)
```

We can see normal distribution of this variable. 

# Univariate Analysis

### What is the structure of your dataset?
Our dataset has tidy data of 4898 observations and 14 variables.
There are no missing values in the dataset, all the data are numeric.

### What is/are the main feature(s) of interest in your dataset?
The main features of interest for me are alcohol and residual sugar, if they are
corellated and their influence on quality

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
I would like to see also the input from volatile acidity and density.

### Did you create any new variables from existing variables in the dataset?
I created new categorical variable 'category' depending on the residual sugar 
content. I used wine classification for labeling wines as dry, medium dry and 
medium.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
I noticed, that the distribution of residual sugar was long-tailed. There was 
one outlier, which value was very far from all the other values and would 
influence our explorations. This outlier was deleted from the dataset.

# Bivariate Plots Section

Let's take a quick look at the correlation between all the variables in our 
dataset

```{r}
ggcorr(wine_new, label = TRUE)
```

We can see strong positive correlation between residual sugar and density and 
medium positive correlations between total sulfur dioxide and density, 
free sulfur dioxide and total sulphur dioxide (this one is easily explained, as 
total sulphur dioxide contains free sulphur dioxide). 
Strong negative correlation is between density and alcohol, medium negative 
correlation is between residual sugar and alcohol.
There is also correlation between alcohol and quality, it is about 0.4.

Let's explore these some of these pairs in more details.

First of all, as we are interested in quality as and important output variable, 
we will explore it through categories with boxplots and frequency polygons

```{r echo=FALSE, message=FALSE, warning=FALSE}

qplot(x = category, y = quality, data = wine_new, geom = 'boxplot') +
  stat_summary(fun.y = "mean", geom = "point", color = "red")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

qplot(x = quality, data = wine_new, geom = 'freqpoly', color = category, 
      binwidth = 0.2)

```      
      
So, we can see, that 50% of dry and medium dry wines are in range 5 to 6. 
75% of medium wines are also in this range.
Mean and median values are approximately 6 for dry and medium dry wines.
for medium wines mean value is 5 and median 5.5

      
Explore the distribution of alcohol through quality, including conditional 
summaries. Also reduce overplotting with transparency.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = quality, y = alcohol), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'blue') +
  geom_line(stat = 'summary', fun.y = mean, color = "red") +
  geom_line(stat = 'summary', fun.y = median, color = "black") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = 0.25), 
            color = "orange") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = 0.75), 
            color = "orange")
```

We can see a strong corellation on the most part of the plot, for quality 5 to 
9. But more poor wines (quality 3 to 5) have almost stable alcohol levels, even 
with small decrease. Let's change varibles between axes and add smoother.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = alcohol, y = quality), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'blue') +
  geom_smooth (method = 'lm', color = "red")
```

This plot shows that wines with higher alcohol have higher quality.
We can check this also with the Pearson's R

```{r echo=FALSE, message=FALSE, warning=FALSE}
cor.test(wine_new$alcohol, wine_new$quality)
```

Deffinitely, there is a positive correlation between alcohol and quality.

Now let's see the distribution of alcohol depending on the category of wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x = alcohol, data = wine_new, geom = 'freqpoly', color = category, 
  binwidth = 0.2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

by(wine_new$alcohol, wine_new$category, summary)
```

It looks like dry wines has wider range of alcohol content.
Medium dry and medium wines in our dataset tend to have lower alcohol content.
Will explore relationship between alcohol and sugar content in later analisys.

Let's see the relation between residual sugar and quality.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = quality, y = residual.sugar), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'orange') +
  geom_line(stat = 'summary', fun.y = mean, color = "red") +
  geom_line(stat = 'summary', fun.y = median, color = "black") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = 0.25), 
            color = "blue") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = 0.75), 
            color = "blue")
```

This plot shows no clear correlation. Let's take a look also from other axis, 
as we did at our previous pair of variables

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar, y = quality), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'orange') +
  geom_smooth (method = 'lm', color = "red")
```

We can say, that these plots show the same distribution of values for different 
quality levels. Most of the wines of any quality have very low sugar levels and 
there are less wines with more sugars. Correlation between these two variable is
very weak.

Finally, let's explore relationship between alcohol and residual sugar.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar, y = alcohol), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'brown')
```

Surely, this is a non-linear correlation, in general we can notice, that 
wines with high alcohol content tend to have low sugars, and wines with 
a lot of sugar have low alcohol content. 
Let's check if we can see a stronger relationship adding various transformations.

```{r echo=FALSE, message=FALSE, warning=FALSE}
plot1 <- ggplot(aes(x = residual.sugar, y = alcohol), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'brown') +
  geom_smooth (method = 'lm', color = "blue")
plot2 <- plot1 + scale_x_log10()
plot3 <- plot1 + scale_x_sqrt()
plot4 <- plot1 + scale_y_log10()
grid.arrange(plot1, plot2, plot3, plot4, ncol = 2)
```

We can see non-linear negative correlation, but none of these scatterplots 
uncover any extra pattern. 
Also let's count Pearson's R to see the strength of the relationship.

```{r echo=FALSE, message=FALSE, warning=FALSE}
cor.test(wine_new$residual.sugar, wine_new$alcohol)
```
So, statistics confirms negative relationship with medium strength (-0.459)

Now let's explore relationship between residual sugar and density

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar, y = density), data = wine_new) + 
  geom_point(position = 'jitter', alpha = 0.1, color = 'orange') + 
  geom_smooth(method = 'lm')
```

This visualization shows a positive correlation between residual sugar and
density. Also we can see again that most of our wines are dry wines, with low 
level of sugar.

Finally, let's explore relationship between density and quality.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(y = density, x = quality), data = wine_new) + 
  geom_point(position = 'jitter', alpha = 0.1, color = 'violet') +
  geom_smooth(method = 'lm')
```

We can see a negative correlation, let's count the Pearson's R for this pair of 
variables.

```{r echo=FALSE, message=FALSE, warning=FALSE}
cor.test(wine_new$density, wine_new$quality)
```

Pearson's R is -0.315. It is not a very strong correlation, but it is worth
further investigation.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

My first interest was to see the relationships between pairs of 3 variables:
alcohol, residual.sugar and quality. Analysis shows positive correlation 
between alcohol and quality, which I will continue to explore in the third 
part of the project. There were no significant relationship between quality and 
residual sugar. Also, negative correlation was found between residual sugar and
alcohol.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

I found a very high correlation between density and alcohol

### What was the strongest relationship you found?
The strongest relatioships are between density and alcohol (-0.8) and density 
and residual sugar (0.8). 


# Multivariate Plots Section

First of all, let's create scatterplot matrices for all the variables we are
interested in in our analysis.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Creating a subset database with only these variables.
wine_subset <- wine_new[, c("density", "residual.sugar", "category", "alcohol", 
                            "quality")]
ggpairs(wine_subset)
```

In the matrices we can see many details. Categorial variable 'category' gives us 
boxplot vizualizations and multiple histograms. Other variables have scatter 
plots. 
Also we can see more detailed correlation coefficients for different pairs of 
variables. As we know from previous analysis and now can see on the matrices, 
there are a strong positive correlation between density and residual sugar 
(0.834) and strong negative correlation between density and alcohol (-0.802).
Alcohol and sugar, as considered before, have non-linear negative correlation.
Alcohol and quality and correlated positively (0.436), the scatterplot shows 
that the correlation is weak.

First, let's explore relation of alcohol, density and category of wine, as we 
already know that all these variables are correlated.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wine_new, aes(x = alcohol, y = density, color = category)) +
  geom_point(alpha = 0.5) +
  stat_ellipse()
  
```

So, the scatterplot confirms the negative correlation between the alcohol and
density for the whole dataset and for every category as well.
Also we can see, that wines which are sweeter have higher density, for the same 
alcohol value.

Let's also create multiple scatterplots to check, if this relationship between 
alcohol and density changes for quality of wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = wine_new, aes(x = alcohol, y = density)) +
  facet_wrap(~quality) +
  geom_point(alpha = 0.05)
```

Some of the scatterplots have few observations, because very good and very 
poor wines are not many in our dataset, but all the scatterplots clearly show 
the same relationship between variables, so it is not corellated with the 
quality of wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Adding 2 y-axis on the plot
# Transforming y-axe for alcohol by /4, so lines create better visualization.
# Reducing bins by rounding values on x axe.
ggplot(wine_new, aes(x = 0.01*round(density/0.01))) +
  geom_line(aes(y = residual.sugar, color = 'Sugar'), stat='summary',             
            fun.y = mean) +
  geom_line(aes(y = alcohol*4, color = 'Alcohol'), stat='summary', 
            fun.y = mean) +
  scale_y_continuous(sec.axis = sec_axis(~./4, name = "Alcohol")) +
  scale_colour_manual(values = c("blue", "red")) +
  labs(y = "Residual Sugar", x = "Density", colour = "Parameter")
  
```

This plot shows the relation between alcohol, residual sugar and density.
There is a positive correlation between density and residual sugar.
Corellation between alcohol and density is negative.
On the visualization we can see 2 almost straight lines, each one of them 
"breaks" at the same point, changing (slightly or more) the inclination.
This point is the density of 1.00, the density of clear water. The wine with 
this density will have a mean alcohol of 9.5 and the mean residual sugar 12.  

Let's explore the relation between descrete variable quality and 2 continuous 
variables: alcohol and residual sugar, by creating boxplots.

```{r}
# Adding 2 y-axis on the plot
# Transforming y-axe for sugar by /3, so lines create better visualization.
ggplot(wine_new, aes(x = factor (quality) )) +
  geom_boxplot(aes(y= alcohol, color = 'alcohol') ) +
  geom_boxplot(aes(y = residual.sugar/3, color = 'Sugar') ) +
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Residual Sugar")) +
  scale_colour_manual(values = c("blue", "red")) +
  labs(y = "Alcohol", x = "Quality", colour = "Parameter")
```

As we can see, wines with low quality (3-4) do not have clear relationship with 
alcohol or sugar. One of the reasons for this can be actually a quality itself. 
If experts decided that these wines were bad, wine could be not balanced and 
have too little sugar (not good grapes), or have added sugar, or have added 
alcohol. Wines with average and above quality have visible trends. Wines with 
higher quality have less sugar and more alcohol.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

I observed some relationships between alcohol and density, alcohol and quality,
alcohol and residual sugar and made multivariable plots to explore them in 
more details. Also I created scatterplot matrices to have a general view of
relationships between variables of my interest.

### Were there any interesting or surprising interactions between features?

Figuring out the relationship between alcohol and density, I was surprised
to see, that sweeteness of the wine has influence on it. For the same amount 
of alcohol more sweet wine will have higher density.

------

# Final Plots and Summary


### Plot One

```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_One}
ggplot(aes(x = alcohol, y = quality), data = wine_new) + 
  geom_jitter(alpha = 0.05, color = 'blue') +
  geom_smooth (method = 'lm', color = "red") +
  labs(title = 'Quality of wine by alcohol content', x = 'Alcohol, %', 
       y = 'Quality')
```

### Description One

This plot shows the relation between quality and alcohol.
We see that wines with higher persentage of alcohol are more likely to have 
higher quality. Red smoother line is showing this tendention.

Alpha = 0.05 is used here to avoid overlapping, and jitter is used for the same
reason, as quality variable is discrete. So we can also see distribution of 
wines in our dataset. Most of the wines have quality 5 and 6, less wines have 
quality 7, and much less wines have lower or higher quality. 

Also we can see that almost all the wines contain 9 to 13% of alcohol, with the 
biggest part to be 9-11%, which is the most common alcohol level for white 
european wines.

### Plot Two

```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}
ggplot(data = wine_new, aes(x = alcohol, y = density, color = category)) +
  geom_point(alpha = 0.5) +
  stat_ellipse() +
  labs(title = 'Alcohol and density by wine category', x = 'Alcohol, %', 
       y = 'Density, g/l', color = 'Wine Category')
  
```

### Description Two

This plot shows relationship between density and alcohol. We can see negative
correlation between these variables, which is explained by the nature of making
alcohol drink. Density of water is 1.0 and density of clear alcohol is 0.783.
So the higher volume alcohol has in the water-alcohol mix, the lower will be 
the density of this mix.
Coloring the plot by wine category we also add the sugar content into this 
relationship. We can see, that general negative corellation is the same
within every category, but the most interesting thing we see - that wines with 
the same alcohol content will have higher density if they are have more sugar. 
F.e. for alcohol content of 9% dry wines will have density approx 0.993 to 
0.997, medium dry 0.996 to 1.001 and medium 0.998 to 1.002.


### Plot Three

```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}
ggplot(wine_new, aes(x = factor (quality))) +
  geom_boxplot(aes(y= alcohol, color = 'Alcohol') ) +
  geom_boxplot(aes(y = residual.sugar/3, color = 'Sugar') ) +
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Residual Sugar, g/l")) +
  scale_colour_manual(values = c("blue", "red")) +
  labs(y = "Alcohol, %", x = "Quality", colour = "Parameter") +
  ggtitle("Alcohol and residual sugar in wine by its quality")
```

### Description Three
This plot shows the relation between quality and 2 values: residual.sugar 
and alcohol. 

We can split visualization into 2 parts. 
First part -  wines with low quality (3-4). They do not have clear relationship 
with alcohol or sugar. One of the reasons for this can be actually a quality 
itself. If experts decided that these wines were bad, wine could be not balanced 
and have too little sugar (not good grapes), or have added sugar, or have added 
alcohol. 
Second part - Wines with average and high quality (5-9). Here we can see clear
positive correlation for alcohol and negative correlation for sugar.
Wines with higher quality have less sugar and more alcohol.

------

# Reflection

During the analysis I made I experienced several important moments.

It is very important to explore individual variables and their distribution 
before exploring relationships.

If a dataset is not big enough, there may be too few observations in some parts,
so the exploration will not be reliable. F.e. in my dataset we had only one 
observation for sweet wine. Deffinitely, you can't rely on it for making 
decisions about category.

Sometimes the visualizations you choose may not reflect the correlation (maybe 
it is a wrong type of plot or wrong binwidth). So it is important not to make 
decision from the first plot, but to try different techniques - reduce 
overplotting, transform variables, and to apply condition summaries. 
Statistics matter. 

The dataset may not always allow us to make a model, because there can be other
variables, which influence the output, but they are not in your dataset.
The quality of wine depends very highly on the quality of grapes, on the type of 
grapes and on the age of the wine. We knew nothing about this. 
It would be nice, if we could have some of this information to explore it
and to try to make a model depending on it.

I had some struggles. It is not easy to find the correct way to visualize the 
data. Making wrong plot may lead to mistakes in interpretation of relationships.
In our dataset I had to work with different types of data (categorical, 
discrete, continuous), each of them needed special approach.

But I was happy when I found the trends and was able to interpretate them. It is 
nice to start with exploring distribution and then to end with multivariable 
analysis. It was interesting to see the relationship between alcohol and quality 
or explore different variables through categories, which I decided to create.
